The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-30 paper.tex
update

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light, $m_{\text{e}}$ electron mass,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe such that CRe is energetic enough to\
produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
We set $\gamma_{\text{max}}$ to be $10^{6}$, corresponding to the cutoff CRe energy $0.5$ GeV.

@@

>>>>

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light, $m_{\text{e}}$ electron mass,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic enough to\
produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
We set $\gamma_{\text{max}}$ to be $10^{6}$, corresponding to the cutoff CRe energy $0.5$ GeV.

@@

% After projection the photon flux at energy $$ is computed ..
